(tentative) Rotational Spectral Unmixing of Exoplanets

### 2017-02-22 paper/main.tex
adding a draft of regularization term
missing figures are added

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[tbh!]
    \begin{center}
\includegraphics[width=\hsize]{mockdata_90deg_3types_t12_lc_noreg.pdf}
\includegraphics[width=\hsize]{mockdata_90deg_3types_t12_lc_reg.pdf}
    \end{center}
    \caption{correlation length $30^{\circ }$. }
\label{fig:noreg}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[bth!]
    \begin{center}
\includegraphics[width=\hsize]{mockdata_90deg_3types_t12_lc_noreg.pdf}
    \end{center}
    \caption{Probability of surface albedo spectra estimated from colors of longitudinal slices, without regularization term (``flat'' prior?). }
\label{fig:noreg}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[tbh!]
    \begin{center}
%\includegraphics[width=\hsize]{mockdata_90deg_3types_t12_lc_noreg.pdf}
\includegraphics[width=\hsize]{mockdata_90deg_3types_t12_lc_reg_l30deg.pdf}
\includegraphics[width=\hsize]{mockdata_90deg_3types_t12_lc_reg_l40deg.pdf}
    \end{center}
    \caption{Upper panel: on the assumption of gaussian process with correlation length $30^{\circ }$. Lower panel: correlation length $40^{\circ }$. }
\label{fig:noreg}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Prior: Gaussian Processes}
%\label{ss:gp}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

A more constraining condition we might impose is the correlation length of the light curves.

%%%
\begin{eqnarray}
&&Posterior 
\\ &&= \prod\limits_{i,j}\left[  \frac{1}{\sqrt{2\pi }\sigma_{ij}} \exp \left\{ - \frac{(d_{ij} - \sum _{lk} W_{il} f_{lk} s_{kj})^2}{2 \sigma _{ij}^2} \right\} \right] \notag \\
&& \;\;\;\;\;\;\;\;\;\; \times \; \mathcal{P} (\{f_{lk}\}) \cdot \mathcal{P}(\{s_{kj}\}) 
\end{eqnarray}
%%%
where $\mathcal{P} (X) $ is a prior for $X$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[tbh!]
    \begin{center}
%\includegraphics[width=\hsize]{mockdata_90deg_3types_t12_lc_noreg.pdf}
\includegraphics[width=\hsize]{IGBP_lon_noreg.pdf}
\includegraphics[width=\hsize]{IGBP_lon_reg_l30deg.pdf}
    \end{center}
    \caption{Probability of surface albedo spectra estimated from colors of longitudinal slices, without (upper) and with (lower) regularization term. The regularization term for the lower panel assumes correlation length $30^{\circ }$. }
\label{fig:noreg}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
